\section{Input and Output}

The Galois ABB allows values to be input, either from public values
or from values known by a single party.
Both protocols are simple, using an approach that is applicable
to RSS schemes in general.

\begin{protocol}[Input]
	\InputGal{x}
	\begin{enumerate}
		\item $P_1$ and $P_2$ set $x_1 = x$.
		\item $P_2$ and $P_3$ set $x_2 = 0$ and 
			$P_3$ and $P_1$ set $x_3 = 0$, 
			where 0 here represents the identity element
			of $\GFtwol$.
		\item $P_i$ sets its share as $(x_{i-1}, x_i)$.
	\end{enumerate}

	\noindent \InputGalFrom{x}{i}:
	\begin{enumerate}
		\item $P_i$ selects $x_1$, $x_2$ at random from $\GFtwol$.
		\item $P_i$ sets $x_3 = x \Gadd x_1 \Gadd x_2$.
		\item $P_i$ sends $(x_{j-1}, x_j)$ to $P_j$
			for $j \in \{i-1, i+1\}$.
		\item $P_{i-1}$ sends $x_{i+1}$ to $P_{i+1}$.
			If $P_{i+1}$ received different values for $x_{i+1}$
			from $P_i$ and $P_{i-1}$, $P_{i+1}$ aborts
			and sends an abort message to all other parties.
		\item If any party receives an abort message, it aborts.
		\item Each party $P_j$ sets its share as $(x_{j-1}, x_j)$.
	\end{enumerate}
\end{protocol}

Note that in the Galois field, each item is its own additive inverse,
that is $x \Gadd x = 0$ for all $x \in \GFtwol$.
This means setting $x_3 = x \Gadd x_1 \Gadd x_2$ is equivalent
to stating that $x_3$ is set such that $x_1 \Gadd x_2 \Gadd x_3 = x$.

Values store in the Galois ABB can be output, either to all parties
or to a single party.

\begin{protocol}[Output]
	\OutputGal{\galois{x}}
	\begin{enumerate}
		\item Let $(x_{i-1}, x_i)$ be the share held by $P_i$.
		\item For each $i \in \{1, 2, 3\}$ (in parallel):
			\begin{enumerate}
				\item $P_i$ and $P_{i+1}$ send $x_i$ to $P_{i-1}$.
				\item If $P_{i-1}$ receives inconsistent values,
					$P_{i-1}$ aborts and sends abort to
					the other parties.
				\item If any party receives an abort message, it aborts.
			\end{enumerate}
		\item Each party computes $x = x_1 \Gadd x_2 \Gadd x_3$.
	\end{enumerate}

	\noindent	\OutputGalTo{\galois{x}}{i}:
	\begin{enumerate}
		\item Let $(x_{j-1}, x_j)$ be the share held by party $P_j$,
			for each $j \in \{1, 2, 3\}$.
		\item $P_{i-1}$ and $P_{i+1}$ send $x_{i+1}$ to $P_i$.
		\item If $P_i$ receives inconsistent messages, $P_i$ aborts
			and sends the abort message to the other parties.
		\item If any party receives an abort message, it aborts.
		\item $P_i$ computes $x = x_1 \Gadd x_2 \Gadd x_3$.
	\end{enumerate}
\end{protocol}



