\section{Non-linear Operations}

Non-linear operations, such as AND and OR, require interaction among the parties. Let $\bit{x}$ represent a sharing of the value $x$, with shares $(t^x_1, s^x_1)$, $(t^x_2, s^x_2)$, $(t^x_3, s^x_3)$ for $P_1, P_2, P_3$, respectively.
Similarly, let $\bit{y}$ represent a sharing of the value $y$, with shares $(t^y_1, s^y_1), (t^y_2, s^y_2), (t^y_3, s^y_3)$ for $P_1, P_2, P_3$, respectively.

\subsection{AND Gates}

We first describe a protocol for securely computing AND gates, where the adversary is allowed to introduce an error bit, as outlined in Section 2.2 of \cite{EC:FLNW17}. The protocol ensures {\it privacy} and requires each party to send only one bit. It consists of two phases:
In the first phase, the parties compute a $3$-out-of-$3$ XOR-sharing of the AND of the input bits. In the second phase, they convert the $3$-out-of-$3$ sharing into the Boolean RSS sharing.

The parties also hold \emph{correlated randomness} $\alpha_1, \alpha_2, \alpha_3$ such that $\alpha_1 \oplus \alpha_2 \oplus \alpha_3 = 0$ generated using {\bf \RandZero}.

\begin{protocol}
    \label{protocol:AndwithError}
    \AndwithError{\bit{x}}{\bit{y}}
    \begin{enumerate}
        \item Each $P_i$ computes $r_i = t^x_i t^y_i \oplus s^x_i s^y_i \oplus \alpha_i$ and sends $r_i$ to $P_{i + 1}$.
        \item Each $P_i$ outputs $(t^z_i, s^z_i)$ where $t^z_i = r_i \oplus r_{i + 2}$ and $s^z_i = r_i$.
    \end{enumerate}
\end{protocol}

It was demonstrated in Lemma $2.4$ of \cite{CCS:AFLNO16} that the resulting shares form a valid and consistent Boolean sharing of either $x \wedge y$ or $(x \wedge y) \oplus 1$.

We now present a protocol for securely computing AND gates without introducing any errors.
Specifically, we include an additional layer of verification at the end to detect any misbehavior by the adversary.

\begin{protocol}
    \label{protocol:AND}
    \And{\bit{x}}{\bit{y}}
    \begin{enumerate}
        \item Each $P_i$ computes $r_i = t^x_i t^y_i \oplus s^x_i s^y_i \oplus \alpha_i$ and sends $r_i$ to $P_{i + 1}$.
        \item Each $P_i$ defines $\bit{z}$ as $(t^z_i, s^z_i)$ where $t^z_i = r_i \oplus r_{i + 2}$ and $s^z_i = r_i$.
        \item Each $P_i$ adds $(\bit{x}, \bit{y}, \bit{z})$ to $\UnverifiedTriples{i}$.
    \end{enumerate}
    Parties output $\bit{z}$.
\end{protocol}

\subsection{OR Gates}

To compute $\bit{x \vee y}$, each $P_i$ computes $(\bit{x} \oplus \bit{y}) \oplus (\bit{x} \wedge \bit{y})$.
