\section{Arithmetic Black Box Model}

The Arithmetic Black Box (ABB) \cite{C:DamNie03} 
is a functionality designed to abstract away secret-sharing.
Rather than keeping track of individual shares which are held by each party,
the ABB is viewed as storing the secret-shared values.
In addition to allowing data to be input into the ABB (implemented by secret-sharing)
and allowing data to be output from the ABB (implemented by secret-share reconstruction),
the ABB allows certain basic operations on values 
(implemented by protocols that take secret-shared inputs and produce secret-shared outputs).

Traditionally, the ABB was viewed as a single entity that held a single type of variable,
using a specific type of secret-sharing.
However, to be \emph{expressive},
we will make use of several variable types
(corresponding, for instance, to the types \textit{bool} and \textit{int}
in standard programming languages).
To be \emph{efficient}, some variable types, will have multiple share representations
(e.g. the Boolean and Arithmetic share representations of non-negative integers).
We therefore view each of these type-representation combinations as a separate ABB,
each supporting different operations according to what is appropriate for the 
given type, and what is reasonably efficient given the representation.
Variables stored in an ABB are represented using square brackets,
with a super-script after the brackets indicating the type-representation 
indicating which ABB is used.
For example $\bit{x}$ indicates that a variable, with public identifier $x$, 
is stored in the BoolBit ABB.
See Table \ref{tab:abb_list} for details.

The \SLCompute platform uses two types of secret sharing.
\emph{Additive secret sharing} is a sharing such that there is one share for each party
and the sum of these shares (in some group) results in the secret.
\emph{Replicated Secret Sharing} (RSS) uses a base additive secret sharing, 
but rather than each party holding a single share, each party holds multiple shares.
(More generally, each party may hold multiple linearly-independent 
affine functions of the shares).
The ABBs each use variants of RSS as the underlying secret sharing to store data;
some protocols for ABB operations also make use of additive secret sharing.
Note that Replicated Secret Sharing is a type of \emph{authenticated}
secret sharing---if a corrupted party modifies its shares this can be 
detected---whereas an Additive secret sharing is \emph{unauthenticated}.
